% !TEX root = ../main.tex
% (this is to make TexShop know where your parent file is)

% The music or sound design is original and innovative. Excellent composition, production and performance. The relationship between the audio and the moving image has been executed very thoughtfully to a professional standard.The audio shows excellent creative insight into the development of audio assets for mobile games or UI.Clear evidence that the ethos, narrative, purpose and/or structure of the game has been considered, embraced and supported by the audio consistently throughout.Excellent work that is distinctive or unique whilst remaining true to the context of the project.

There is no mention in the brief of what kind of game this is, aside from it being a "fantasy epic", so I'd argue that you can take some pretty big liberties with it.

In the B section [00:28--00:42], the only non-major chord in that sequences plays when the camera is inside the well. This is a bit of foreshadowing for what the blacksmith does with all of his gentleman callers.

Likewise, the same section is repeated in the mask making section [01:53--02:07], which again ties it back to the original appearance of the well and the ultimate fate of the mask.

There's a little dies irae quote in the (left-panned) tremolo guitar as the knight falls to his knees [01:35--01:39], as a little nod to how the dies irae is often used in film/games music to represent death.

This was an attempt at \textit{sideways writing}\footnote{That is, take something you like and start with that, modifying it to be your own}, and I think it was partially successful. However, I don't think I quite managed to break free of the mold, and that some parts (the "chorus" [01:25--01:38] especially; compare [guns for hire timestamps]) are too close for comfort.

However, I think the harmonic hitpoints are well-suited to the sequence and that the substitutions I made to the "Guns for Hire" chords work well in context.
