% !TEX root = ../main.tex
% anything appart from comments in this file will appear in the Research Section of the text.
% do your main writing here.
% use \autocite for bibliography and \ref to cite internal figures and tables

% Detailed research into the style/form in question, referencing a wide range of relevant source material. Clear evidence of critical reflection and analysis of sources that informs both aesthetic and functional aspects to the work.

The main inspiration for this was S1E6 of \textit{Arcane}\autocite[27:30--31:20]{arcane-s1e6} (2021), "When These Walls Come Tumbling Down". In the episode's climax, the protagonists Vi and Caitlyn flee from antagonist Silco's goons and Silco's plans come crashing down around him (figuratively and literally). This is accompanied not by frenetic action music, but by Woodkid's "Guns for Hire", a sombre, yet hopeful, downtempo track, consisting primarily of voice, guitar, and strings.

I think this choice of music is so effective for the juxtaposition of the action on the screen with the tempo and feel of the song. As Vi's long-estranged sister lights a flare for Vi to find her, the music swells into a sombre, yet hopeful chorus [29:30], and even as Silco viciously and repeatedly kicks one of his subordinates bloody, the same song continues.

This, of course, is nothing new in film and TV, and this kind of juxtaposition between the on-screen action and the soundtrack is a tried and tested formula. It's cliche, but that means it's effective.

Now, a TV-show might not be the most obvious choice of reference for a video game cutscene, but the same kind of juxtaposition can work just as well here. In fact, you could take "Guns for Hire" exactly as it is presented on the soundtrack album and play it over the cutscene, and it works quite well as-is.

But still, using a song to score a video game opening cutscene is --- as far as I know --- unusual. However, using songs in video games has become more common as the hardware limitations of game consoles have lessened. Darren Korb has had success doing just that with, among others, \textit{Bastion} \autocite{8-bitmusictheoryThatsWhyBastion2026} (2011), \textit{Hades} (2020) and \textit{Hades II} (2025). Additionally, Lorien Testard's score for \textit{Clair Obscur: Expedition 33} (2025) uses sung vocals extensively throughout the game to great effect.

\subsection*{"Guns for Hire" highlights / analysis}

"Guns for Hire" uses a lot of clever/interesting harmonic shifts (rough chart/analysis in \hyperref[appendixB]{Appendix~B}) that I have taken the liberty of either slightly modifying or stealing outright.

It's ostensibly in B-flat minor, but the occasional major second chord (C major in this case) is featured prominently [00:16; 01:21] (mirrored in my track [00:19; 00:43]\footnote{The second example is technically a minor seventh chord on the major seventh of the scale, but the upper triad is the same major triad on the second degree of the scale}), which gives a sense of unease and foreboding --- likely because it's audibly chromatic and contains the tritone.

Another very cool trick is the sudden tritone jumps [00:28] which take the listener to an entirely different harmonic place, often brightening the sound. The same trick is used for the transition to the B section [00:28; 01:54] in my track.

Finally, the vocals landing on the major seventh of the major sixth chord  [00:03; 01:07] is a repeated motif that paints the track in a bittersweet light. The minor tonic chord to the major sixth chord really has a pretty hopeful sound, but with the vocals landing hard on the major seventh, it adds a delicate piece of instability to the whole thing.
